---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# functionsnashid

<!-- badges: start -->
<!-- badges: end -->

During the data exploration phase, developers write repeated code to investigate the summary view based on different categories. The goal of this package is to avoid writing [boilerplate code](https://en.wikipedia.org/wiki/Boilerplate_code) during the data exploration phase. This package implements counting the number of observations per category in a given dataset and returns the top observations. 

## Installation

This package is not in the CRAN yet. You can install the development version of `functionsnashid` from the [GitHub](https://github.com/stat545ubc-2021/functionsnashid) repository with:

``` r
devtools::install_github("stat545ubc-2021/functionsnashid")
```

## Basic Example

Please check `?count_by_category` for a more detailed explanation of the function. Now we demonstrate the basic usage of the function. In the following example, we get the number of games per genre from the steam_games dataset.

1. **Results in descending order by default:**

```{r}
suppressMessages(library(tidyverse))
suppressMessages(library(datateachr))
library(functionsnashid)

games <- steam_games %>%
  select(id, name, genre, publisher, developer, original_price, release_date, all_reviews) %>%
  separate_rows(genre, sep = ",", convert = TRUE)

count_by_category(steam_games, genre, 5)
```

2. **Results in ascending order:**

```{r}
count_by_category(steam_games, genre, 5, FALSE)
```

## More Examples with Different Datasets

Here we would demonstrate the usage of the function `count_by_category` to explore different dataset:

#### Get the count of trees per genus in the `vancouver_trees` dataset.

We see Acer genus i.e. family of Maple trees are the most common in vancouver.

```{r}
count_by_category(vancouver_trees, genus_name, 5)
```

#### Get the count of apartment buildings per property type in the `apt_buildings` dataset. 

```{r}
count_by_category(apt_buildings, property_type, 5)
```
#### What `heating_types` are common in in the `apt_buildings` dataset?

```{r}
count_by_category(apt_buildings, heating_type, 5)
```
