---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# functionsnashid

<!-- badges: start -->
<!-- badges: end -->

The goal of functionsnashid is to implement counting the number of observations per category. 

## Installation

You can install the released version of functionsnashid from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("functionsnashid")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/functionsnashid")
```
## Example

This is a basic example which shows you how to solve a common problem.

In the following example, we get the number of games per genre from the steam_games dataset.

```{r example}
library(functionsnashid)
library(tidyverse)
library(datateachr)

games <- steam_games %>%
  select(id, name, genre, publisher, developer, original_price, release_date, all_reviews) %>%
  separate_rows(genre, sep = ",", convert = TRUE)

count_by_category(games, genre, 5)

```

Now we demonstrate the usage of the function:

**Results in descending order by default:**

```{r}
count_by_category(games, genre, 5)
```

**Results in ascending order:**

```{r}
count_by_category(games, genre, 5, FALSE)
```

## Exercise 3: Include examples (15 points)

Demonstrate the usage of your function with a few examples. Use one or more new code chunks, describing what you're doing.

Note: If you want to deliberately show an error, you can use `error = TRUE` in your code chunk option.

### Demonstrate the Usage of the Function:

Here we would demonstrate the usage of the function `count_by_category` to explore different dataset:

#### Get the count of trees per genus in the `vancouver_trees` dataset.

We see Acer genus i.e. family of Maple trees are the most common in vancouver.

```{r}
count_by_category(vancouver_trees, genus_name, 5)
```

#### Get the count of apartment buildings per property type in the `apt_buildings` dataset. 

```{r}
count_by_category(apt_buildings, property_type, 5)
```
#### What `heating_types` are common in in the `apt_buildings` dataset?

```{r}
count_by_category(apt_buildings, heating_type, 5)
```
